quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-09-17 paper-quollr.Rmd
Updated find_pts

scurve_umap_scaled <- scurve_model_obj$nldr_obj$scaled_nldr
tr_from_to_df_scurve <- scurve_model_obj$trimesh_data
df_bin_centroids_scurve <- scurve_model_obj$model_2d
df_bin_scurve <- scurve_model_obj$model_highd
hex_grid_scurve <- scurve_model_obj$hb_obj$hex_poly
counts_df_scurve <- scurve_model_obj$hb_obj$std_cts

@@

```{r, echo=TRUE}
bin_configs <- calc_bins_y(
  nldr_obj = scurve_umap_obj, 
  b1 = 15, 
  q = 0.1)

@@

```{r, echo=TRUE}
hb_obj <- hex_binning(
  nldr_obj = scurve_umap_obj, 
  b1 = 15, 
  q = 0.1)
```

@@

```{r}
#| label: code-illustration
# Code to draw illustration for notation
## hexagon binning to have regular hexagons
hb_obj_notation <- hex_binning(
  nldr_obj = scurve_umap_obj, 
  b1 = 9, 
  q = 0.1)

@@

```{r hex-param, fig.cap="The components of the hexagon grid illustrating notation.", out.width="50%", fig.align='center', fig.pos='H'}

@@

```{r, echo=TRUE}
all_centroids_df <- gen_centroids(
  nldr_obj = scurve_umap_obj, 
  b1 = 15, 
  q = 0.1
  )

@@

```{r, echo=TRUE}
umap_hex_id <- assign_data(
  nldr_obj = scurve_umap_obj, 
  centroids_data = all_centroids_df
  )

@@

The `find_pts()` function extracts the list of data point identifiers (`ID`) assigned to each hexagon in the NLDR space.

@@

```{r, echo=TRUE}
pts_df <- find_pts(
  scaled_nldr_hexid = umap_hex_id
  )

@@

df_bin_centroids_limb <- tsne_limb_obj$model_2d
df_bin_limb <- tsne_limb_obj$model_highd
trimesh_data_limb <- tsne_limb_obj$trimesh_data
tsne_limb_scaled <- tsne_limb_obj$nldr_obj$scaled_nldr

@@

df_bin_centroids_limb <- tsne_best_limb_obj$model_2d
df_bin_limb <- tsne_best_limb_obj$model_highd
trimesh_data_limb <- tsne_best_limb_obj$trimesh_data
tsne_limb_scaled <- tsne_best_limb_obj$nldr_obj$scaled_nldr

>>>>

scurve_umap_scaled <- scurve_model_obj$nldr_scaled_obj$scaled_nldr
tr_from_to_df_scurve <- scurve_model_obj$trimesh_data
df_bin_centroids_scurve <- scurve_model_obj$model_2d
df_bin_scurve <- scurve_model_obj$model_highd
hex_grid_scurve <- scurve_model_obj$hb_obj$hex_poly
counts_df_scurve <- scurve_model_obj$hb_obj$std_cts

@@

```{r, echo=TRUE}
bin_configs <- calc_bins_y(
  nldr_scaled_obj = scurve_umap_obj, 
  b1 = 15, 
  q = 0.1)

@@

```{r, echo=TRUE}
hb_obj <- hex_binning(
  nldr_scaled_obj = scurve_umap_obj, 
  b1 = 15, 
  q = 0.1)
```

@@

```{r, eval=FALSE}
#| label: code-illustration
# Code to draw illustration for notation
## hexagon binning to have regular hexagons
hb_obj_notation <- hex_binning(
  nldr_scaled_obj = scurve_umap_obj, 
  b1 = 9, 
  q = 0.1)

@@

```{r hex-param, fig.cap="The components of the hexagon grid illustrating notation.", out.width="50%", fig.align='center', fig.pos='H', eval=FALSE}

@@

```{r, echo=TRUE}
all_centroids_df <- gen_centroids(
  nldr_scaled_obj = scurve_umap_obj, 
  b1 = 15, 
  q = 0.1
  )

@@

```{r, echo=TRUE}
umap_hex_id <- assign_data(
  nldr_scaled_obj = scurve_umap_obj, 
  centroids_data = all_centroids_df
  )

@@

The `group_hex_pts()` function extracts the list of data point identifiers (`ID`) assigned to each hexagon in the NLDR space.

@@

```{r, echo=TRUE}
pts_df <- group_hex_pts(
  scaled_nldr_hexid = umap_hex_id
  )

@@

df_bin_centroids_limb <- tsne_limb_obj$model_2d
df_bin_limb <- tsne_limb_obj$model_highd
trimesh_data_limb <- tsne_limb_obj$trimesh_data
tsne_limb_scaled <- tsne_limb_obj$nldr_scaled_obj$scaled_nldr

@@

df_bin_centroids_limb <- tsne_best_limb_obj$model_2d
df_bin_limb <- tsne_best_limb_obj$model_highd
trimesh_data_limb <- tsne_best_limb_obj$trimesh_data
tsne_limb_scaled <- tsne_best_limb_obj$nldr_scaled_obj$scaled_nldr
